Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web

### 2024-11-25 autovi_paper.qmd
reproducibility with quarto and source code link

The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi). The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).

>>>>

The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi) and [https://github.com/TengMCing/autovi_web](https://github.com/TengMCing/autovi_web) respectively. The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).

This paper is reproducibly written using Quarto [@Allaire_Quarto_2024] powered by Pandoc version [@MacFarlane_Pandoc] and pdfTeX. The full source code to reproduce this paper is available at <https://github.com/TengMCing/autovi_paper>.
